Model

### 2019-11-18 stats/model.Rmd
update model

# Model (nesting within participant)

## Prepare data

data_comb_log <- read_csv("../data/combination.csv") %>%
  mutate(nov_int = novel_params$Intercept,
         nov_slope = novel_params$age_num,
         prior = ifelse(alignment == "congruent", plogis(nov_int + nov_slope* age),1-plogis(nov_int + age * nov_slope)))

## Model code

### Prior model

### Combination Model

@@

var familiars = levels(data, "familiar")
var subjects = levels(data, "subid")
var priorSubjects = levels(priorData, "subid")

@@

        var itemLineParameters = all_item_parameters[row.familiar]

@@

Infer({model,
      samples: 50000,
      burn: 50000,
      verbose: T,
      lag: 1,
      verboseLag: 1000,
      method: "incrementalMH",
      onlyMAP: true,
      callbacks: [callback]});
'
```

@@

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log, prior_data = prior_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 2,
  cores = 2,
  packages = c("webppl_packages/webppl-sample-writer")
)

```
## Model comparison

@@

>>>>

# Model

## Combination Model

@@

var familiars = levels(data, "item")
var subjects = levels(data, "subid")
var priorSubjects = levels(priorData, "subid")

@@

@@

Infer({model,
      samples: 1,
      burn: 1,
      verbose: T,
      lag: 1,
      verboseLag: 1000,
      method: "incrementalMH",
      onlyMAP: true,
      callbacks: [callback]});
'
```

@@

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb, prior_data = prior_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 2,
  cores = 2,
  packages = c("webppl_packages/webppl-sample-writer")
)
```

# Ignore below for now

## Model comparison

@@

## Base model

## Prior model
